\textls[-0]{\thetitle}

### 2023-03-17 canonicitymodel.tex
Save Canonicity Model.
Save Canonicity model.

\newcommand{\Glued}[1]{\ensuremath{{#1}^\bullet}}
\newcommand{\GluedPi}[2]{\ensuremath{\Pi^\bullet({#1},{#2})}}
\newcommand{\GSubstExt}[2]{\ensuremath{{#1},^\bullet{#2}}}
\newcommand{\Gpair}[2]{\ensuremath{({#1},^\bullet{#2})}}
\newcommand{\Gfst}[1]{\ensuremath{\texttt{fst}^\bullet~{#1}}}
\newcommand{\Gsnd}[1]{\ensuremath{\texttt{snd}^\bullet~{#1}}}
\newcommand{\Gsub}[2]{\ensuremath{{#1}\!\left[{#2}\right]^\bullet}}
\newcommand{\Glam}[1]{\ensuremath{\lambda^\bullet({#1})}}
\newcommand{\Gapp}[1]{\ensuremath{\texttt{app}^\bullet({#1})}}
\newcommand{\GSubstWeak}[1]{\ensuremath{(\texttt{p}^\bullet)^{#1}}}
\newcommand{\GLSigAdd}[3]{\ensuremath{\nu^{+\bullet}({#1},{#2},{#3})}}
\newcommand{\GCaseSig}[3]{\ensuremath{\texttt{CaseTy}^\bullet({#1},{#2},{#3})}}
\newcommand{\Gmodel}[1]{\ensuremath{{({#1})}^c}}
\newcommand{\GEl}[1]{\ensuremath{\Glued{\texttt{El}}({#1})}}
\newcommand{\Gwcode}[1]{\ensuremath{\Glued{\texttt{W}}({#1})}}
\newcommand{\GSubstId}{\ensuremath{\GSubstWeak{0}}}

@@

\newcommand{\GTy}[2]{\ensuremath{\Glued{\texttt{Ty}}_{#1}~{#2}}}
\newcommand{\GCon}[1]{\ensuremath{\Glued{\texttt{Con}}_{#1}}}
\newcommand{\GTm}[2]{\ensuremath{\Glued{\texttt{Tm}}~{#1}~{#2}}}
\newcommand{\GMWSig}[3]{\ensuremath{{\texttt{WSig}^C}_{#1}^{#3}~{#2}}}
\newcommand{\GWSig}[3]{\ensuremath{{\Glued{\texttt{WSig}}}_{#1}^{#3}~{#2}}}

There are actually more \emph{internal} type-theoretic construction to we need:

@@

These four sets are collecting the glued interpretation:
basically the point is, for each well-typed type $\goodType{\Gm}{T}{j}$,  we have its denotation $\denotesCC{T} \in \GTy{j}{\denotesCC{\Gm}}$; and for each well-typed term $\goodTerm{\Gm}{t}{T}$, we have its denotation $\denotesCC{t} \in \GTm{\denotesCC{\Gm}}{\denotesCC{T}}$.

@@

  & \Gmodel{\Gsub{\Gapp{\Gsub{\Gapp{\Recproj{j}{\sub{\denotesCC{\lkg}}{\Glued{\gm}}}}}{\GSubstExt{\GSubstId}{\Glued{a}}}}}{\GSubstExt{\GSubstId}{\Glam{\Glued{\rho}}}}}(\epsilon)(\star) \\

@@

   \text{ and also } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \quad ,\Glued{R} = \denotesCC{"R"}, \Glued{B} = \wsigproj{j}{2}{\Glued{\wsig}}

@@

\begin{align*}
  "Inductive"~\CWmodel &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    \CWsup &: j < N \to \Glued{a} \in \GTm{\Glued{\cdot}}{\wsigproj{j}{1}{\Glued{\wsig}}} \\
    & \to \Glued{b} \in (\GTm{(\Glued{\cdot} \Glued{,} \Gsub{\wsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\GSubstId}{\Glued{a}}}) }{\Gsub{\GEl{\Gwcode{\wsig}}}{\GSubstWeak{1}}}) \to \CWmodel~\Glued{\wsig}~\Wsup{j}{\wsig}{a}{b}
\end{align*}
... and its eliminator principle $\CWrec$. 
\begin{align*}
  \CWrec \  &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to 
    (P : \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{k})  \\
    & \to [j < N \to  \Glued{a} \in \GTm{\Glued{\cdot}}{\wsigproj{j}{1}{\Glued{\wsig}}} \\ 
    & \quad \quad \to 
    b \in (\GTm{({\cdot} {,} \sub{\wsigproj{j}{2}{{\wsig}}}{\SubstExt{\SubstId}{{a}}}) }{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}}) \\ 
    & \quad \quad \to b^C : (\Glued{\gm} \in (\Glued{\cdot} \Glued{,} \sub{\wsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\SubstId}{\Glued{a}}}) \to P~\sub{b}{\Gmodel{\Glued{\gm}}}) \\
    & \quad \quad \to P~(\Wsup{j}{\wsig}{a}{b}) ] \\
    & \to \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \to \CWmodel~\Glued{\wsig}~t \to P~t \\
  \CWrec \  & \Glued{\wsig}~P~f~t~(\CWsup~\Glued{a}~\Glued{b}) = f~\Glued{a}~b~(\lambda \Glued{\gm}. \CWrec~P~f~(\sub{b}{\Gmodel{\Glued{\gm}}})~(b^C~\Glued{\gm}))
\end{align*}

>>>>

\newcommand{\Glued}[1]{\ensuremath{{#1}^\bullet}}
\newcommand{\GluedPi}[2]{\ensuremath{\Pi^\bullet({#1},{#2})}}
\newcommand{\GSubstExt}[2]{\ensuremath{{#1},^\bullet{#2}}}
\newcommand{\Gpair}[2]{\ensuremath{({#1},^\bullet{#2})}}
\newcommand{\Gfst}[1]{\ensuremath{\texttt{fst}^\bullet~{#1}}}
\newcommand{\Gsnd}[1]{\ensuremath{\texttt{snd}^\bullet~{#1}}}
\newcommand{\Gsub}[2]{\ensuremath{{#1}\!\left[{#2}\right]^\bullet}}
\newcommand{\Glam}[1]{\ensuremath{\lambda^\bullet({#1})}}
\newcommand{\Gapp}[1]{\ensuremath{\texttt{app}^\bullet({#1})}}
\newcommand{\GSubstWeak}[1]{\ensuremath{(\texttt{p}^\bullet)^{#1}}}
\newcommand{\GLSigAdd}[3]{\ensuremath{\nu^{+\bullet}({#1},{#2},{#3})}}
\newcommand{\GCaseSig}[3]{\ensuremath{\texttt{CaseTy}^\bullet({#1},{#2},{#3})}}
\newcommand{\Gmodel}[1]{\ensuremath{{({#1})}^c}}
\newcommand{\GEl}[1]{\ensuremath{\Glued{\texttt{El}}({#1})}}
\newcommand{\Gwcode}[1]{\ensuremath{\Glued{\texttt{W}}({#1})}}
\newcommand{\GSubstId}{\ensuremath{\GSubstWeak{0}}}
\newcommand{\Gwsigproj}[3]{\ensuremath{\Glued{{\texttt{w}\pi^{#1}_{\texttt{#2}}}}({#3})}}
\newcommand{\GRecproj}[2]{\ensuremath{\Glued{{\texttt{R}\pi^{#1}}}({#2})}}

@@

\newcommand{\GTy}[2]{\ensuremath{\Glued{\texttt{Ty}}_{#1}~{#2}}}
\newcommand{\GCon}[1]{\ensuremath{\Glued{\texttt{Con}}_{#1}}}
\newcommand{\GTm}[2]{\ensuremath{\Glued{\texttt{Tm}}~{#1}~{#2}}}
\newcommand{\GSub}[2]{\ensuremath{\Glued{\texttt{Sub}}~{#1}~{#2}}}
\newcommand{\GMWSig}[3]{\ensuremath{{\texttt{WSig}^C}_{#1}^{#3}~{#2}}}
\newcommand{\GWSig}[3]{\ensuremath{{\Glued{\texttt{WSig}}}_{#1}^{#3}~{#2}}}

There are actually more \emph{internal} type-theoretic construction that we need:

@@

and $\GSub{\Glued{\Gm}}{\Glued{\Dl}} \coloneq \sum_{\goodSub{\Gm}{\delta}{\Dl}} \prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)} \Gmodel{\Glued{\Dl}}(\delta \circ \gm) $

These four sets are collecting the glued interpretation:
basically the point is, for each well-typed type $\goodType{\Gm}{T}{j}$,  we have its denotation $\denotesCC{T} \in \GTy{j}{\denotesCC{\Gm}}$; and for each well-typed term $\goodTerm{\Gm}{t}{T}$, we have its denotation $\denotesCC{t} \in \GTm{\denotesCC{\Gm}}{\denotesCC{T}}$, and etc.

% Note that, for arbitrary $\Glued{\Gm} \in \GCon{k}$, we can consider it as $\Glued{\gm}$ as an element of $\GSub{\Glued{\cdot}}{}$

@@

  & \Gmodel{\Gsub{\Gapp{\Gsub{\Gapp{\GRecproj{j}{\sub{\denotesCC{\lkg}}{\Glued{\gm}}}}}{\GSubstExt{\GSubstId}{\Glued{a}}}}}{\GSubstExt{\GSubstId}{\Glam{\Glued{\rho}}}}}(\epsilon)(\star) \\

@@

   \text{ and also } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \quad ,\Glued{R} = \denotesCC{"R"}, \Glued{B} = \Gwsigproj{j}{2}{\Glued{\wsig}}

@@

\begin{align*}
  "Inductive"~\CWmodel &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    \CWsup &: j < N \to \Glued{a} \in \GTm{\Glued{\cdot}}{\wsigproj{j}{1}{\Glued{\wsig}}} \\
    & \to \Glued{b} \in (\GTm{(\Glued{\cdot} \Glued{,} \Gsub{\wsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\GSubstId}{\Glued{a}}}) }{\Gsub{\GEl{\Gwcode{\Glued{\wsig}}}}{\GSubstWeak{1}}}) \to \CWmodel~\Glued{\wsig}~\Wsup{j}{\wsig}{a}{b}
\end{align*}
... and its eliminator principle $\CWrec$. 
\begin{align*}
  \CWrec \  &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to 
    (P : \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{k})  \\
    & \to [j < N \to  \Glued{a} \in \GTm{\Glued{\cdot}}{\Gwsigproj{j}{1}{\Glued{\wsig}}} \\ 
    & \quad \quad \to 
    \goodTerm{({\cdot} {,} \sub{\wsigproj{j}{2}{{\wsig}}}{\SubstExt{\SubstId}{{a}}}) }{b}{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}} \\ 
    & \quad \quad \to b^C : (\Glued{\gm} \in (\Glued{\cdot} \Glued{,} \sub{\Gwsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\SubstId}{\Glued{a}}}) \to P~\sub{b}{\Gmodel{\Glued{\gm}}}) \\
    & \quad \quad \to P~(\Wsup{j}{\wsig}{a}{b}) ] \\
    & \to \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \to \CWmodel~\Glued{\wsig}~t \to P~t \\
  \CWrec \  & \Glued{\wsig}~P~f~t~(\CWsup~\Glued{a}~\Glued{b}) = f~\Glued{a}~b~(\lambda \Glued{\gm}. \CWrec~P~f~(\sub{b}{\Gmodel{\Glued{\gm}}})~(b^C~\Glued{\gm}))
\end{align*}
